Recursion
==========

## Loop of Fibonacci Numbers
#### Given Example:
```{r}
fibLoop <- function(n) {
    Ffirst <- 0
    Fsecond <- 1
    for (k in 2:n) {
        newF <- Ffirst + Fsecond
        Ffirst <- Fsecond
        Fsecond <- newF
    }
    return(newF)
}

fibLoop(5)
fibLoop(20)
```
#### Loop where the state is maintained by a vector of n+1 slots, with the first two slots initialized to 0 and 1 respectively:
```{r}
fibLoop2<-function(n){
  sofar=c(0,1)
  for(k in 3:n){
  sofar[k]<-sofar[k-1]+sofar[k-2]
  sofar[k+1]<-sofar[k]+sofar[k-1]
  }
  return(sofar[k+1])
  }

fibLoop2(5)
fibLoop2(20)
```
#### Returns all fibonacci numbers n and below:
```{r}
fibLoop2<-function(n){
  sofar=c(0,1)
  for(k in 3:n){
  sofar[k]<-sofar[k-1]+sofar[k-2]
  sofar[k+1]<-sofar[k]+sofar[k-1]
  }
  return(sofar)
  }

fibLoop2(5)
fibLoop2(20)
```

## A Recursive structure for Fn
#### Given Example:
```{r}
fibRecurse <- function(n) {
    if (n == 1) {
        return(1)
    } else {
        if (n == 0) 
            return(0)
    }
    thisF <- fibRecurse(n - 1) + fibRecurse(n - 2)
    return(thisF)
}

fibRecurse(5)
fibRecurse(20)
```
#### More concise way:
```{r}
fib1 <- function(n) {
    if (n < 2) 
        return(n)
    return(fib1(n - 1) + fib1(n - 2))
}

fib1(5)
fib1(20)
```

## Exercises
#### Write a recursive function to add up the numbers from n to zero:
```{r}
addNSeq <- function(n) {
  if(n==1){
    return(1)}
  else{
    if(n==0){
      return(0)
    }
  }
  sum <- addNSeq(n-1)+n
  return(sum)
  }

addNSeq(3)
addNSeq(5)

```
#### Looping Version:
```{r}
addNSeqLoop<-function(n){
  sum <- 0
  for(k in 1:n){
    sum <- n-k + sum
  }
  return(sum+n)
}

addNSeqLoop(3)
addNSeqLoop(5)
```
#### Simple vectorized operational version:
```{r}
addNSeqSimple<-function(n){
  vect <- 1:n
  return(sum(vect))
}

addNSeqSimple(3)
addNSeqSimple(5)
```
#### Write a recursive function to add up all the numbers in a vector:
```{r}
addRecursively <- function(v) {
  if(length(v)==1){
    return(v[1])
  }
  sum <- addRecursively(v[-length(v)])+v[length(v)]
  return(sum)
  }

addRecursively(c(1,2,3))
addRecursively(c(5,7,9))
```
#### Loop Version:
```{r}
addWithLoop<-function(v){
  sum<-0
  for(k in 1:length(v)){
    sum <- v[k]+sum
  }
  return(sum)
}

addWithLoop(c(1,2,3))
addWithLoop(c(5,7,9))
```
#### Simple vectorized operational version:
```{r}
addSimple<-function(v){
  sum(v)
}

addSimple(c(1,2,3))
addSimple(c(5,7,9))
```



